% Copied from http://www-twiki/ClimateConsultancy/LegalDisclaimer 05.01.2012
% Last reviewed by Legal: October 2011

\section*{Disclaimer}

\begin{itemize}
\item This document is published by the Met Office on behalf of the
  Secretary of State for Business, Energy and Industrial Strategy, HM
  Government, UK. Its content is covered by {\copyright} Crown
  Copyright {\number\year}.
 
\item This document is published specifically for the readership and
  use of {\CustomerName} and may not be used or relied upon by any
  third party, without the Met Office's express written permission.
 
\item The Met Office aims to ensure that the content of this document
  is accurate and consistent with its best current scientific
  understanding.  However, the science which underlies meteorological
  forecasts and climate projections is constantly evolving.
  Therefore, any element of the content of this document which
  involves a forecast or a prediction should be regarded as our best
  possible guidance, but should not be relied upon as if it were a
  statement of fact.  To the fullest extent permitted by applicable
  law, the Met Office excludes all warranties or representations
  (express or implied) in respect of the content of this document.
 
\item Use of the content of this document is entirely at the reader's
  own risk. The Met Office makes no warranty, representation or
  guarantee that the content of this document is error free or fit for
  your intended use.
 
\item Before taking action based on the content of this document, the
  reader should evaluate it thoroughly in the context of his/her
  specific requirements and intended applications.
 
\item To the fullest extent permitted by applicable law, the Met
  Office, its employees, contractors or subcontractors, hereby
  disclaim any and all liability for loss, injury or damage (direct,
  indirect, consequential, incidental or special) arising out of or in
  connection with the use of the content of this document including
  without limitation any and all liability:

\begin{itemize}
\item relating to the accuracy, completeness, reliability,
  availability, suitability, quality, ownership, non-infringement,
  operation, merchantability and fitness for purpose of the content of
  this document;
 
\item relating to its work procuring, compiling, interpreting,
  editing, reporting and publishing the content of this document; and
 
\item resulting from reliance upon, operation of, use of or actions or
  decisions made on the basis of, any facts, opinions, ideas,
  instructions, methods, or procedures set out in this document.
\end{itemize} 
 
\item This does not affect the Met Office's liability for death or
  personal injury arising from the Met Office's negligence, nor the
  Met Office's liability for fraud or fraudulent misrepresentation,
  nor any other liability which cannot be excluded or limited under
  applicable law.
 
\item If any of these provisions or part provisions are, for any
  reason, held to be unenforceable, illegal or invalid, that
  unenforceability, illegality or invalidity will not affect any other
  provisions or part provisions which will continue in full force and
  effect.
\end{itemize}

